---
title: "trump cluster comparisons"
output: html_notebook
Note: create network graph using retweet. embed six clustering algorithms
Author: Thomas E. Keller
---

Following a recommendation from (insert name) that Loni received from a research workshop she attended, we will try several different clustering methods in igraph, as compared to the single clustering method available in gephi. Loni made a reference to a paper (link?) that found that the Girvan-Newman (2004) method implemented in Gephi was the most effective out of 4 compared. 

What scale?

```{r netprep}
library(dplyr)
library(igraph)
library(readr)
setwd('~/trump_rtweet')
df=read_csv('rtweet_justfornetwork_051118.csv')

df=filter(df,is_retweet==1)
df=df[complete.cases(df),]
df$status_id=as.character(df$status_id)
df=distinct(df,status_id,.keep_all=TRUE)
#remove donald trump account, it warps the network because everyone on the right follows it
df=filter(df,screen_name!="realDonaldTrump" & retweet_screen_name!="realDonaldTrump")


```

# making the retweet network

After filtering out non-retweet tweets, we make a dataframe of all retweets as from-to relationships, and add a weight column to them.

Separately, we make labels out of the unique set of names in the edge list.

deg_subset is a quantile cutoff function to take the top x% of accounts based on their degree distribution. So, if you give it deg_subset(0.001, graph) then it will return the top .001% of accounts according to the degree distribution.

Finally, we try some different clustering methods so we can compare them to the default method in gephi (cluster_louvain in igraph).

```{r network}
# make the graph
#filter to only count those posts that have actually been retweeted
edges = data.frame(from=df$screen_name,to=df$retweet_screen_name,stringsAsFactors = F)  %>% group_by(from,to) %>% summarize(value = n())

# Build a df for nodes
nodes <- data.frame(id = unique(c(edges$from, edges$to)),
                    label = unique(c(edges$from, edges$to)),
                    stringsAsFactors = F) %>% tbl_df

library(igraph)
rt_graph <- make_empty_graph() + vertices(nodes$id) +
  edges(as.vector(rbind(edges$from, edges$to)), weight = edges$value)


#takes the cutoff as a fraction (usually .01-.001) equilivent to the 
deg_subset<-function(cutoff,g){
  rc=1-cutoff
  dfv=data.frame(V=as.vector(V(g)),screen_name=V(g)$name,degree(g))
  names(dfv)[3]="degree"
  dfv=cbind(dfv,quantile=cut(dfv$degree,
                             breaks=quantile(dfv$degree,probs=c(0,rc,1)),
                             labels=c("Bottom99",'Top1'),include.lowest=T))
  dfv$quantile=as.character(dfv$quantile)
  dfv2=arrange(dfv,desc(quantile))
  dfv3=dfv2[dfv2$quantile=='Top1',]
  sg=induced_subgraph(g,dfv3$V)
  res=list(g=sg,df=dfv3)
  return(res)
}

#2619 total acccounts
res=deg_subset(.001,rt_graph)
res_df=res$df
sub_g=res$g



res_df=cbind(res_df,mod_blouv=m_b$membership,mod_label=m_l$membership)
res_df=arrange(res_df,desc(degree))

write_csv(res_df,"top_001p_trump051618_rtweet.csv")

#not needed anymore (did at the top)
#sub_g=delete_vertices(sub_g,"realDonaldTrump")

sub_gc=as.undirected(sub_g, mode = "collapse") 

m_e=cluster_leading_eigen(sub_gc) # wants undirected  (duh its an eigen method) still has problems?
m_c=cluster_walktrap(sub_gc)
m_b=cluster_louvain(sub_gc)
m_l=cluster_label_prop(sub_gc)
m_i=cluster_infomap(sub_gc)
m_f=cluster_fast_greedy(sub_gc)
#m_bt=cluster_edge_betweenness(sub_g) Don't run this one, it is EXTREMELY slow compared to other methods


res_df=cbind(res_df,mod_blouv=m_b$membership,mod_label=m_l$membership)


#normally we can just directly save the subgraph without
#having to add these extra attributes
#this was the first time I had to do this extra step
#however, this is how and where you save these extra variables to send to gephi

sub_gc2 = sub_gc %>% set_vertex_attr("mod_walktrap",value=m_c$membership) %>% 
  set_vertex_attr("mod_blouvain",value=m_b$membership) %>%
  set_vertex_attr("mod_label",value=m_l$membership) %>%
  set_vertex_attr("mod_infomap",value=m_i$membership) %>%
  set_vertex_attr("mod_eigen",value=m_e$membership) %>%
  set_vertex_attr("mod_greedy",value=m_f$membership)
  

list.graph.attributes(sub_gc2)

#final output for gephi
library(rgexf)
rg=igraph.to.gexf(sub_gc2)
f=file("rtweet_6clusters_051118.gexf")
writeLines(rg$graph, con = f)
close(f)
library(stringr)



```

